0/1 Knapsack

### 2015-03-11 Programming Project C/01knapsack.tex
fixed off by one issue in dynamic solution, added table in paper

%% BEGIN TESTING
\section{Testing}
\subsection{Testing Plan and Results}
All arrays used in testing are Java ArrayList<Integer> except for $tab$ in the dynamic solution, which is a primitive Java nested array. All times are recorded in milliseconds using a stopwatch class borrowed from Robert Sedgwick and Kevin Wayne \cite{stopwatch}
It is important to note that the stopwatch lass used takes the elapsed real-time between the start of the call to the knapsack solution and the end of that call as opposed to taking the elapse processor-time because these tests were run on a multi-core computer.
When the number of elements was below 100, the size of the knapsack was 50; when values of 100 and greater were used the size of the knapsack was $2n$ where $n$ is the number of elements. For example, if the number of elements was 100, the size of the knapsack was 200, in order so the knapsack was sure to be able to make reasonable comparisons.
In the table below, times are given as averages out of 10 trials in milliseconds.
\newline
\captionof{table}{Greedy Solution Real-Time Run-Time}
\begin{center}
\begin{tabular}{|l|l|l|}
\hline Number of Elements & Size of Knapsack & Time \\
\hline 0 & 50 & 0.0 \\
\hline 1 & 50 & 0.0 \\
\hline 10 & 50 & 0.0006 \\
\hline %% TODO: Finish table
\end{tabular}
\end{center}
%% TODO: Make table for dynamic solution
%% TODO: You need to implement a testing plan testing the correctness of the two algorithms!

@@

When the dynamic solution was executed with values of anything above $n = 100000$ and $c = 200000$ Java gave a "Out Of Memory Error: Java heap space". This can be attributed the extreme number of elements being stored in $tab$. The computer's system monitor reported RAM usage at 95\%. Unfortunately, this issue cannot be aided.

>>>>

%% BEGIN TESTING
\section{Testing}
\subsection{Testing Plan and Results}
All arrays used in testing are Java ArrayList<Integer> except for $tab$ in the dynamic solution, which is a primitive Java nested array. All times are recorded in milliseconds using a stopwatch class borrowed from Robert Sedgwick and Kevin Wayne \cite{stopwatch}
It is important to note that the stopwatch lass used takes the elapsed real-time between the start of the call to the knapsack solution and the end of that call as opposed to taking the elapse processor-time because these tests were run on a multi-core computer.
When the number of elements was below 100, the size of the knapsack was 50; when values of 100 and greater were used the size of the knapsack was $2n$ where $n$ is the number of elements. For example, if the number of elements was 100, the size of the knapsack was 200, in order so the knapsack was sure to be able to make reasonable comparisons.
In the table below, times are given as averages out of 10 trials in milliseconds.
\newline
\captionof{table}{Greedy Solution Real-Time Run-Time}
\begin{center}
\begin{tabular}{|l|l|l|}
\hline Number of Elements & Size of Knapsack & Time \\
\hline 0 & 50 & 0.0 \\
\hline 1 & 50 & 0.0 \\
\hline 10 & 50 & 0.0006 \\
\hline 100 & 200 & 0.0043 \\
\hline 1000 & 2000 & 0.0231 \\
\hline 10000 & 20000 & 0.252 \\
\hline 100000 & 200000 & 59.1176 \\
\hline
\end{tabular}
\end{center}
\captionof{table}{Dynamic Solution Real-Time Run-Tim}
\begin{center}
\begin{tabular}{|l|l|l|}
\hline 0 & 50 & 0.0001 \\
\hline 1 & 50 & 0.0 \\
\hline 10 & 50 & 0.0002 \\
\hline 100 & 200 & 0.0119 \\
\hline 1000 & 2000 & 0.0356 \\
\hline 10000 & 20000 & 1.9243 \\
\hline
\end{tabular}
\end{center}
%% TODO: You need to implement a testing plan testing the correctness of the two algorithms!

@@

When the dynamic solution was executed with values of anything above $n = 10000$ and $c = 20000$ Java gave a "Out Of Memory Error: Java heap space". This can be attributed the extreme number of elements being stored in $tab$. The computer's system monitor reported RAM usage at 95\%. Unfortunately, this issue cannot be aided.
